Reionization Planck 2018 Notes

### 2020-06-25 results/notes.tex
Updates from Overleaf

\begin{figure}
\includegraphics[width=0.65\textwidth]{results/direct_mcmc/two_parameter_model/tauhi_taulo_chains/pl18_tanh_highz_test2_run1_tri.png}
\caption{Direct MCMC chains of the two-parameter model with \tauhi and \taulo: triangle plot of \tauhi and \taulo.
}
\label{fig:two_parameter_model_2D_plot}
\end{figure}

 \begin{figure}
\includegraphics[width=0.65\textwidth]{   results/direct_mcmc/pl18_plots_zmax30/plot_pub_tau_gtz_dz_0p1_pl18_pc_zmax30_pliklite_srollv2_0930_and_pl18_tanh_post_pliklite_srollv2_with_added_two_parameter_ML_xe_full.pdf}
\caption{PC zmax = 30 vs tanh chains with plik lite and srollv2, with ML model from two-parameter model for \tauhi restricted to $>$ 0.02 (ML model: \tauhi = 0.0206, \taulo = 0.0414).
}
\label{fig:two_parameter_model_ML}
\end{figure}

@@

>>>>

\begin{figure}
\includegraphics[width=0.65\textwidth]{results/direct_mcmc/two_parameter_model/tauhi_taulo_chains/pl18_tanh_highz_test2_run1_tri.png}
\caption{Direct MCMC chains of the two-parameter model with \tauhi and \taulo: triangle plot of \tauhi and \taulo. The marginalized 1D constraints are \taulo = $0.0516 \pm 0.0076$, \tauhi = $0.0100 \pm   0.0066$. The ML model is \taulo = 0.0543 and \tauhi = 0.0054 corresponding to $z_{\rm re} = 7.68$ and $x_{e, \mathrm{min}} = 0.021$.
}
\label{fig:two_parameter_model_2D_plot}
\end{figure}

 \begin{figure}
\includegraphics[width=0.65\textwidth]{   results/direct_mcmc/pl18_plots_zmax30/plot_pub_tau_gtz_dz_0p1_pl18_pc_zmax30_pliklite_srollv2_0930_and_pl18_tanh_post_pliklite_srollv2_with_added_two_parameter_ML_xe_full.pdf}
\caption{PC zmax = 30 vs tanh chains with plik lite and srollv2, with ML model from two-parameter model for \tauhi restricted to $>$ 0.02 (ML model: \tauhi = 0.0206, \taulo = 0.0414). (Note: I need to update the xe(z) curve to be that of the best-fit model in the best-fit search with tau_hi = 0.02 fixed.)
}
\label{fig:two_parameter_model_ML}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.65\textwidth]{cosmomc_kde/direct_mcmc_vs_python_kde_and_cosmomc_kde_tanh_tau.png}
\caption{LATEST (to be debugged) -- Added cosmomc KDE version of tau posterior computed with f = 0.14, against python versions with f = 0.1, 0.12, 0.14. They do not agree ... (Note: need to make sure python version had the same covariance matrix, and length of chain ...)
}
\label{fig:}s
\end{figure}

\begin{figure}
\includegraphics[width=0.65\textwidth]{cosmomc_kde/direct_mcmc_vs_python_kde_and_cosmomc_kde_tanh_tau.png}
\caption{LATEST (to be debugged) -- Added cosmomc KDE version of tau posterior computed with f = 0.14, against python versions with f = 0.1, 0.12, 0.14. They do not agree ... (Note: need to make sure python version had the same covariance matrix, and length of chain ...)
}
\label{fig:}s
\end{figure}
